---
title: "Visualize Data"  
output: github_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE ) 

library(tidyverse)
```



```{r}
mpg
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!
can add any notes in the your turn. put the code into the chunk.
ggplot2 not working so we forced an update
the first part initializes the graphic
after each + it is adding a new layer (always put + at the end of the line not the beginning of the next)
the geom_point is adding the points and aes(aesthetics) is telling it what to put where
every plot starts with this bare template(not including mpg, point, and displ and hwy)
first decision is what is the geom(etries) ours was point


```{r}  
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.
I just replaced point with the word boxplot

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.
don't have to write mapping, can just write aes = ...
we want a different binwidth so we can find how to change it by going to help-> and typing geom_histogram and looking for codes

```{r}
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.
inside aes is the values; outside it all the aesthetics we want to change
type the color in quotes

```{r}
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy), binwidth = 2, fill = "pink")
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment. 
changing aesthetics is to draw peoples eyes to what we want them to notice
shape only has 6 XD
alpha changes transparency
outside the aes applies to everything
anything with one particular variable has to be inside aes

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 0.3)  

```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}

```

## Quiz

What will this code do?

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy))
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```